% --- OBJECTIVES AND GOALS --- %
\section{Objectives and goals achieved}

The main objective of this project is a critical review and comparison on the
most popular solvers for Lambert's problem. To achieve this purpose, the
whole process was divided into the following key objectives:

\begin{itemize}

  \item \textbf{Review of Lambert's problem timeline.}
        The historical background showed which authors have proposed solutions
        to the problem and when they did so. Important scientific
        figures arose when carrying out this part of the research.

  \item \textbf{Analysis of problem's geometry, solutions and singularities.}
        A deep review on the problem was performed by listing all the
        different solutions their nature.  Multi-revolution transfers were also
        considered together with limiting cases.

  \item \textbf{Collection of modern algorithms.}
        A mathematical comparison between all of them was carried out taking
        into account four factors: the selected iteration variable, the
        numerical method used, proposed initial guess and the way of
        computing the velocity vectors.

  %\item \textbf{Implementation of a new method.}
  %      A new routine based on the analytical solution to the conic equations
  %      was implemented for the first time and compared against previous
  %      solvers too.

  \item \textbf{Performance framework and comparison.}
        All computer algorithms were coded under the same programming language,
        so no undesired additional performance was introduced.  Contour
        maps relating the transfer angle, time of flight and number of
        iterations to achieve desired accuracy were computed to
        illustrate the robustness of each routine.

  \item \textbf{Discussion on the obtained results.}
        Strengths and weaknesses of each algorithm were exposed with previous
        analysis. All the results were collected and studied to raise
        new ideas regarding solutions performance of future solvers.

\end{itemize}

The implementation of all collected algorithms lead to the creation of a
Lambert's problem solvers hub in the form of a software
library\footnote{Available under public license at:
  https://github.com/jorgepiloto/lamberthub}, which will be useful for other
authors when testing new numerical procedures.
