\section{Final conclusion}

This work presented a performance comparison between modern Lambert's problem
solvers, considering the direct-arc transfer scenario and not the
multi-revolution one.

A review of Lambert's problem was presented in chapter \ref{sec:review_lambert}.
The problem was presented from both a geometrical and analytical point of view
using as example the first solution to the problem devised by Lagrange.

Chapter \ref{sec:modern_solvers} was devoted to modern solvers. The different
steps involved during the computation of the problem's solution were presented
together with a solvers classification based on the free-parameter. Among the
selected solvers,  \cite{gauss1809}, \cite{battin1984}, \cite{gooding1990},
\cite{avanzini2008}, \cite{arora2013}, \cite{vallado2013} and \cite{izzo2015}
were the chosen ones. Only the direct-arc transfer and not the multi-revolution
scenario was considered in this analysis.

Then, in chapter \ref{performance_chapter}, different metrics such us the
required number of iterations, time per iteration and total computation time for
a particular combination of non-dimensional time and transfer angle were used to
test the accuracy and robustness of each solver. Contour plots were generated
showing these results. Finally, the performance was based considering first the
convergence of a solver, the total computation time and the iteration workload.
With all these conditions, previous solvers were sorted in performance as
\cite{izzo2015}, \cite{arora2013}, \cite{gooding1990}, \cite{battin1984},
\cite{avanzini2008}, \cite{vallado2013}, \cite{gauss1809}.

